Model Samples Processing

### 2020-02-18 stats/model.Rmd
add developmental mixture model

x_fb <- sample(1:length(unique(model_pred_prag_fb$iteration)), 200)

@@

@@

@@

com_global_params <- bind_rows(
  global_params%>%mutate(model="pragmatic"),
  global_params_fb%>%mutate(model="fullBayes")
)

@@

```{r}
plot_model_comp <- bind_rows(
plot_model_prag_line,
plot_model_prag_line_fb
)

>>>>

x_mm <- sample(1:length(unique(model_pred_mm$iteration)), 200)

model_pred_mm_line_mm <- model_pred_mm%>%
  filter(iteration %in% x_mm)%>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

@@

```{r}
ggsave("../graphs/pred_mm_model_data.pdf", width = 10, height = 3, scale = 1)
```

@@

```{r}
ggsave("../graphs/cor_model_data_mm.pdf", width = 8, height = 3.5, scale = 1)
```

# Developmental Mixture model

item_params_dmm <- readRDS("../saves/item_params_dmm.rds")

global_params_dmm <- readRDS("../saves/global_params_dmm.rds")

item_sigma_dmm <- readRDS("../saves/item_sigma_dmm.rds")

mixture_dmm <- readRDS("../saves/mixture_dmm.rds")

#### summaries
item_params_summary_dmm <- item_params_dmm %>%
  group_by(item, parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

global_params_summary_dmm <- global_params_dmm %>%
  group_by (parameter,type)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

```{r}
plot_item_params_dmm <- ggplot(item_params_dmm, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter ~ item, scales = 'free')+
  theme_few()+
  theme(legend.position = "bottom")

plot_item_params_dmm
```

plot_global_params_dmm <- ggplot(global_params_dmm, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(type ~ parameter, scales = 'free')+
  theme_few()+
  theme(legend.position = "bottom")

plot_global_params_dmm
```

```{r}
plot_item_sigma_dmm <- ggplot(item_sigma_dmm, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(type ~ parameter, scales = 'free')+
  theme_few()

plot_item_sigma_dmm
```

```{r}
plot_mixture_dmm <- ggplot(mixture_dmm, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("value")+
  facet_grid(~type)+
  xlim(0,1)+
  theme_few()

plot_mixture_dmm
```

```{r}
plot_sem_know_dmm <- item_params_summary_dmm%>%
  select(-uci,-lci)%>%
  spread(parameter, -item) %>%
  left_join(expand.grid(
      age = unique(me_model_data$age),
      item = unique(me_model_data$item)), .) %>%
  mutate(sem_know = plogis(intercept + slope * age)) %>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

ggplot(plot_sem_know_dmm, aes(x = age+2, y= sem_know, col = item, group = item))+
  geom_line(size = 1)+
  ylab("Semantic knowledge")+
  xlab("Age")+
  ylim(0,1)+
  theme_few()+
  scale_colour_viridis_d(name = "familiar object")
```

```{r}
model_pred_dmm <- readRDS("../saves/model_pred_dmm.rds")

plot_model_pred_dmm <- model_pred_dmm%>%
  group_by(alignment, item, age)%>%
  summarise(mean = estimate_mode(pred),
            ci_lower = hdi_lower(pred),
            ci_upper = hdi_upper(pred))

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  geom_line(data = plot_model_pred_dmm, aes(x=age+2,y = mean, col = alignment), size = 1)+
  geom_ribbon(data = plot_model_pred_dmm, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol()+
  scale_fill_ptol()

x_dmm <- sample(1:length(unique(model_pred_dmm$iteration)), 200)

model_pred_line_dmm <- model_pred_dmm%>%
  filter(iteration %in% x_dmm)%>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(data = model_pred_line_dmm, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .1)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, span = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F, col = F)+ 
  scale_colour_ptol(name = NULL)

```{r}
ggsave("../graphs/pred_mm_model_data.pdf", width = 10, height = 3, scale = 1)
```

cor_mix_dmm <- readRDS("../saves/model_pred_dmm.rds")%>%
  mutate(age = as.numeric(age) + min(data_comb$age_num),
         age = cut(age,
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model,alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

plot_cor_model_pred_dmm <- cor_mix_dmm %>%
  left_join(binnned_data)

ggplot(data = plot_cor_model_pred_dmm,aes(x = model_mean, y = data_mean, col = alignment)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
  geom_point(size = 1.5, stroke = 1, pch = 5)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(~age)+
  theme_few() + 
  scale_colour_ptol(name ="Alignment")+
  guides(col = F)
```

```{r}
ggsave("../graphs/cor_model_data_mm.pdf", width = 8, height = 3.5, scale = 1)
```

@@

com_global_params <- bind_rows(
  global_params%>%mutate(model="pragmatic"),
  global_params_fb%>%mutate(model="fullBayes"),
  global_params_mm%>%mutate(model="mixture")
)

@@

```{r}
plot_model_comp <- bind_rows(
plot_model_prag_line,
plot_model_prag_line_fb,
plot_model_prag_line_mm
)

### 2020-02-18 stats/model_sample_processing.Rmd
add developmental mixture model

>>>>

# developmental mixture model

model <- bind_rows(
 fread("../webppl/output/samples-fullBayes-devMixtureModel-reFactor-noRandomEffects_mcmc-200_burn100_lag1_chain1.csv",header = T)%>%mutate(chain = 1),
 # fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain2.csv",header = T)%>%mutate(chain = 2),
 # fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain3.csv",header = T)%>%mutate(chain = 3),
 # fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 4),
 # fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 5),
 # fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 6)
)

saveRDS(item_params, "../saves/item_params_dmm.rds")

saveRDS(global_params, "../saves/global_params_dmm.rds")

saveRDS(item_sigma, "../saves/item_sigma_dmm.rds")

mixture<- model %>%
  filter(b == "mixtureComponent")%>%
  select(b,c,g,chain)%>%
    rename(parameter = b,
           type = c,
         value = g)

saveRDS(mixture, "../saves/mixture_dmm.rds")

model_pred_prag <- model %>%
  filter(a == "modelPrediction",
         b == "devMixtureModel")%>%
  select(-a, -h, -c)%>%
  rename(model = b, 
         alignment = d,
         item = e,
         age = f, 
         pred = g)

saveRDS(model_pred_prag, "../saves/model_pred_dmm.rds")
